Prediction of the 2020 Presidential Election

### 2020-11-03 outputs/paper/paper.Rmd
made changes to discussion

with that background knowledge in mind, what do our poll results indicate? From Figure(\@ref(fig:survey_election_results)), we gather that Trump has a very slight lead. Multiple other polls have shown Biden to be in the lead(FiveThirtyEight, 2020). Now there are a few reasons as to why we may not want to use poll results to predict elections. Polls have of late garnered a lot of criticism due to their incorrect predictions of the 2016 Federal election results[@citeAapor]. Note that while they got the ultimate results wrong, they did get the popular vote prediction correct[@citeAapor].Nearly every national poll that year had Hillary Clinton winning, with some estimates of her having a 3% point lead[@citeAapor]. Ultimately, she won the popular vote by 2.1%. However, as mentioned previously, the US does not use a popular vote system. At the state level, the polls became less effective, indicating a Clinton lead again[@citeAapor]. State level polls do translate over to the electoral college a bit more effectively than national polls do. Another reason we may not want to overly rely on polls is yet another cautious tale from the 2016 election season. In that season, polls had over-represented college-graduates, a group that was more likely to vote for Clinton, thus tipping the scales even more in favour of Clinton[@citeAapor]. Capturing this over-representation is key to effectively predicting an election. As mentioned in the results section, some results were intentionally shown as their distributions and then their voting preferences. This was done to elucidate the effect of a difference in representation, akin to  the difference of representation of educated voters between polled data and actual populations. 
From figure(\@ref(fig:age)), there is a clear shift in the distribution of ages. The increased representation of ages 65+ would likely predict a Trump win. Our model coefficient results also indicate that someone being in the oldest age group is more likely to vote for Trump, though significance is only slightly off. With an effectively older population compared to the Nationscape polling data, we can conclude that we would be likely see more votes for Trump coming out of our ACS group. Similarly, when looking at sex, we observe that there are more women in our ACS dataset than there are men, which is the opposite of the distribution found in the Nationscape data. Our model coefficient results again suggest that men are more likely to vote for Trump, and since we have more women in the ACS data, we would expect a higher percentage of Biden votes. This is further supported by other research that suggests that Trump has lost favour with white suburban women, a group he previously was well percevied by[@conroy2020]. A lot of models during the 2016 election season suggested a Clinton win, one of the few models that predicted a Trump win was a model that used MRP[@2016election]. It is worth mentioning that MRP isn't some sort of magic bullet as a few other MRP models during that time still predicted a Clinton win within the electoral college[@2016election]. How do current models fair? The primary model suggests that Trump has a 91% change of winning, in spite of Trump trailing Biden in the polls[@norpoth_2020].

Overall, our model predicts a Trump majority. The

@@

Weaknesses and next steps should also be included.

>>>>

with that background knowledge in mind, what do our poll results indicate? From Figure(\@ref(fig:survey_election_results)), we gather that Trump has a very slight lead. Multiple other polls have shown Biden to be in the lead(FiveThirtyEight, 2020). Now there are a few reasons as to why we may not want to use poll results to predict elections. Polls have of late garnered a lot of criticism due to their incorrect predictions of the 2016 Federal election results[@citeAapor]. Note that while they got the ultimate results wrong, they did get the popular vote prediction correct[@citeAapor].Nearly every national poll that year had Hillary Clinton winning, with some estimates of her having a 3% point lead[@citeAapor]. Ultimately, she won the popular vote by 2.1%. However, as mentioned previously, the US does not use a popular vote system. At the state level, the polls became less effective, indicating a Clinton lead again[@citeAapor]. State level polls do translate over to the electoral college a bit more effectively than national polls do. Another reason we may not want to overly rely on polls is yet another cautious tale from the 2016 election season. In that season, polls had over-represented college-graduates, a group that was more likely to vote for Clinton, thus tipping the scales even more in favour of Clinton[@citeAapor]. Capturing this over-representation is key to effectively predicting an election. As mentioned in the results section, some results were intentionally shown as their distributions and then their voting preferences. This was done to elucidate the effect of a difference in representation, akin to  the difference of representation of educated voters between polled data and actual populations. 
From figure(\@ref(fig:age)), there is a clear shift in the distribution of ages. The increased representation of ages 65+ would likely predict a Trump win. Our model coefficient results also indicate that someone being in the oldest age group is more likely to vote for Trump, though significance is only slightly off. With an effectively older population compared to the Nationscape polling data, we can conclude that we would be likely see more votes for Trump coming out of our ACS group. Similarly, when looking at sex, we observe that there are more women in our ACS dataset than there are men, which is the opposite of the distribution found in the Nationscape data. Our model coefficient results again suggest that men are more likely to vote for Trump, and since we have more women in the ACS data, we would expect a higher percentage of Biden votes. This is further supported by other research that suggests that Trump has lost favour with white suburban women, a group he previously was well perceived by[@conroy2020]. A lot of models during the 2016 election season suggested a Clinton win, one of the few models that predicted a Trump win was a model that used MRP[@2016election]. It is worth mentioning that MRP isn't some sort of magic bullet as a few other MRP models during that time still predicted a Clinton win within the electoral college[@2016election]. How do current models fair? The primary model suggests that Trump has a 91% change of winning, in spite of Trump trailing Biden in the polls[@norpoth_2020].

Overall, our model predicts a Trump majority. The model predicts a win in 32 states and a close call in 10 other states. However, it is important to again caution that this is still the popular vote.

@@

One key weakness in our model is the way we present the results with regards to
